Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-06 paper/paper.tex
adjusted acknowledgments

\author[1]{Alistair B. Russell}
\author[1]{Jacob R. Kowalsky}
\author[1,2,3*]{Jesse D. Bloom}
\affil[1]{Basic Sciences Division and Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, United States}
\affil[2]{Department of Genome Sciences, University of Washington, Seattle, United States}
\affil[3]{Howard Hughes Medical Institute, Fred Hutchinson Cancer Research Center, Seattle, United States}

@@

\section{Acknowledgments}
We thank Cole Trapnell, Jason Underwood, Robert Bradley, Daniel Stetson, and AJ Velthuis for helpful suggestions.
We thank Andy Marty and the Fred Hutch Genomics Core for performing the deep sequencing.
We thank Katherine Xue, David Bacsik, and Hannah Itell for comments on the manuscript.
This work was supported by the NIAID of the NIH under grant R01 AI127893 and a Burroughs Wellcome Fund Young Investigator in the Pathogenesis of Infectious Diseases grant to JDB.
ABR was supported by a postdoctoral fellowship from the Damon Runyon Cancer Research Foundation.
JRK was supported by a Washington Research Foundation Undergraduate Research Fellowship and a Mary Gates undergraduate research scholarship from the University of Washington.
JDB is an Investigator of the Howard Hughes Medical Institute.
The funders had no role in study design, data collection and interpretation, or the decision to submit the work for publication.

>>>>

\author[1]{Alistair B. Russell}
\author[1,2,3*]{Jesse D. Bloom}
\affil[1]{Basic Sciences Division and Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, United States}
\affil[2]{Department of Genome Sciences, University of Washington, Seattle, United States}
\affil[3]{Howard Hughes Medical Institute, Fred Hutchinson Cancer Research Center, Seattle, United States}

@@

\section{Acknowledgments}
We thank Cole Trapnell, Jason Underwood, Robert Bradley, Daniel Stetson, AJ Velthuis, and Katherine Xue for helpful suggestions.
We thank Andy Marty and the Fred Hutch Genomics Core for performing the deep sequencing.
This work was supported by the NIAID of the NIH under grant R01 AI127893 and a Burroughs Wellcome Fund Young Investigator in the Pathogenesis of Infectious Diseases grant to JDB.
ABR was supported by a postdoctoral fellowship from the Damon Runyon Cancer Research Foundation.
JDB is an Investigator of the Howard Hughes Medical Institute.
The funders had no role in study design, data collection and interpretation, or the decision to submit the work for publication.
